Operator evolution from the similarity renormalization group and the Magnus expansion

### 2019-08-28 Notes/Operator_evolution/operator_evolution.tex
Update operator_evolution.tex
Updated revision history and graphicspath.
No changes

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% File: operator_evolution.tex
%
% Author: A. J. Tropiano (tropiano.4@osu.edu)
% Date: August 23, 2019
%
% Draft of paper on SRG operator evolution and the Magnus expansion.
%
% Revision history:
%	...
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

% Packages
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{bm}
\usepackage[font=small,skip=0pt]{caption} % For captions on figures and tables
\usepackage{cellspace}
\usepackage{color}
\usepackage{enumerate}
\usepackage{epsfig}
\usepackage[figuresright]{rotating}
\usepackage{float}
\usepackage{hyperref} % For clickable links to sections within table of contents
\usepackage{graphicx}
\graphicspath{{../../Figures/Operator_evolution/}} % Setting the graphics path
\graphicspath{{../../Figures/SRG_operator_evolution/}}
\usepackage{physics} % For bra-ket notation
\usepackage{siunitx}
\usepackage[caption=false]{subfig} % For sub-figures

@@

\noindent{%
-- Comparison of potential evolution with different regulators, orders, generators.
}
\\
-- Universality.
\\
-- Discussion of high cutoffs, block-diagonal generator at high cutoffs, and how it handles spurious bound states.
\\
-- Use high cutoffs to transition to Magnus test problem.
\\
-- Example figure. EM N$^3$LO potential.
%
\begin{figure}[H]
	\centering
	\subfloat[]{%
	\includegraphics[clip,width=0.9\columnwidth]{potential_contours_kvnn10_3S1_Wegner}%
	}

	\subfloat[]{%
	\includegraphics[clip,width=0.9\columnwidth]{potential_contours_kvnn10_3S1_Block-diag2,00}%
	}

	\subfloat[]{%
	\includegraphics[clip,width=0.9\columnwidth]{potential_contours_kvnn10_3S1_Block-diag3,00}%
	}
	\caption{Matrix elements of the Entem-Machleidt N$^3$LO non-local potential $V_{\lambda}(k, k')$ SRG-evolving in $\lambda$ right to left under transformations with the Wegner generator (a) and block-diagonal generators decoupling at $\Lambda=2$ and $3$ fm$^{-1}$ (b and c).}
	\label{potential_contours_kvnn10_3S1}
\end{figure}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% File: operator_evolution.tex
%
% Author: A. J. Tropiano (tropiano.4@osu.edu)
% Date: August 23, 2019
%
% Draft of paper on SRG operator evolution and the Magnus expansion.
%
% Revision history:
%	08/28/19 --- Started outlining and added pieces from old notes.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

% Packages
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{bm}
\usepackage[font=small,skip=0pt]{caption} % For captions on figures and tables
\usepackage{cellspace}
\usepackage{color}
\usepackage{enumerate}
\usepackage{epsfig}
\usepackage[figuresright]{rotating}
\usepackage{float}
\usepackage{hyperref} % For clickable links to sections within table of contents
\usepackage{graphicx}
\graphicspath{{../../Figures/}} % Setting the graphics path
\usepackage{physics} % For bra-ket notation
\usepackage{siunitx}
\usepackage[caption=false]{subfig} % For sub-figures

@@

\noindent{%
-- Comparison of potential evolution with different regulators, orders, generators.
}
\\
-- Universality.
\\
-- Discussion of high cutoffs, block-diagonal generator at high cutoffs, and how it handles spurious bound states.
\\
-- Use high cutoffs to transition to Magnus test problem.
\\
-- Example figure. EM N$^3$LO potential.
%
\begin{figure}[H]
	\centering
	\subfloat[]{%
	\includegraphics[clip,width=0.9\columnwidth]{SRG_operators/potential_contours_kvnn10_3S1_Wegner}%
	}

	\subfloat[]{%
	\includegraphics[clip,width=0.9\columnwidth]{SRG_operators/potential_contours_kvnn10_3S1_Block-diag2,00}%
	}

	\subfloat[]{%
	\includegraphics[clip,width=0.9\columnwidth]{SRG_operators/potential_contours_kvnn10_3S1_Block-diag3,00}%
	}
	\caption{Matrix elements of the Entem-Machleidt N$^3$LO non-local potential $V_{\lambda}(k, k')$ SRG-evolving in $\lambda$ right to left under transformations with the Wegner generator (a) and block-diagonal generators decoupling at $\Lambda=2$ and $3$ fm$^{-1}$ (b and c).}
	\label{potential_contours_kvnn10_3S1}
\end{figure}
